No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System

### 2019-02-10 ms-temp.tex
6 parameter mcmc

\title{That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b}

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows, 78 Mount Auburn Street, Cambridge, MA 02138}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\author{Rodrigo Luger}
\author{Megan Bedell}

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b I, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations, using an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$. The addition of a moon does not significantly improve the fit quality. We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon). We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices. We conclude that future follow-up efforts for exomoons should focus on alternate targets.

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}. Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit \citep{teachey18b}. The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.

Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method. Motivated by this result, in this work we perform an independent fit to the HST light curve.

@@

\section{Observations and Data Reduction} \label{sec:data}
The Kepler-1625 system was observed with 26 continuous \HST\ orbits on 28 - 29 October, 2017 (Program GO 15149: PI: A. Teachey). The observations used the Wide Field Camera 3 (WFC3) G141 grism in staring mode, which fixed the spectrum in a constant position on the detector.  At the beginning of the visit, there was a single exposure taken with the F130N filter, which is used to determine the position of the spectral trace. The following exposures used the G141 grism with the \texttt{SPARS25}, \texttt{NSAMP}=15 readout pattern (exposure time of 290.8 seconds; 9 exposures per orbit). For additional description of the observation design, see \cite{teachey18b}.

We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.  This software has yielded consistent results with multiple independent pipelines \citep[e.g.][]{knutson14b, spake18}.  We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI). The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples. In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude. We also discard exposures taken during the South Atlantic Anomaly passage (exposures 107, 116, 125, and 126).

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.  The best was $450  < \mathrm{X} < 574$, and $522 < \mathrm{Y} < 536$, where X and Y are physical pixels in the spectral and spatial direction, respectively.

We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.  The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.  For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).  We measured and subtracted the background from the data array as described in \ref{sec:background}. For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).  The initial pixel mask marked all pixels as good.

In brief, optimal extraction is an iterative procedure with the following steps. First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($7.5 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 7.5$.  To create the broadband transit light curve, we sum each spectrum over all wavelengths.

@@

\subsection{Pointing Drift Measurement}
The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel/day) due to the spacecraft's pointing drift. This drift can change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons are recorded. To enable a correction for this effect, we measured the position of the spectrum over time.

To measure shifts in the spatial direction, we first summed each \texttt{flt} image over all columns (which we dub the ``column sum"). We used the first exposure in the visit as a template, and for each subsequent exposure, we used least-squares minimization to calculate the shift in pixels that minimized the difference between its column sum and the template. The shifts are a fraction of a pixel, so we used the NumPy \texttt{interp} routine to do linear interpolation on a sub-pixel scale. The WFC3 point spread function is undersampled, so we convolved each column sum with a 4-pixel-wide Gaussian  before the interpolation \citep[following][]{deming13}.

@@

Figure\,\ref{fig:shifts} shows the best fit shifts. Over the entire 26-orbit visit, the maximum shift is less than 0.2 pixel in the spatial direction and 0.3 pixel in the spectral direction. The largest shift occurs after orbit 14, when the telescope reacquired the guide stars.

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
    \caption{Top: raw data from this work (blue) compared to TK18 (red). Bottom: the difference in raw photoelectron counts between the data sets. The moon ingress identified by TK18 is marked by the dotted gray line.}
\label{fig:raw}
\end{figure}

\section{Analysis}
The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}. The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius $R_*$, the planet radius $R_\mathrm{planet}$, the time of central transit $t_\mathrm{planet}$, and the planet inclination $i$. For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$. We allowed the moon period to vary from 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.

The models also fixes several parameters that are poorly constrained by the light curve shape. For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.  We also fixed the moon mass and eccentricity to zero.  For both the no-moon and moon models, we fixed the planet's orbital period to 287.378949 days \citep{teachey18b}. We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.

\begin{figure*}
\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
    \caption{Best fit models compared to normalized transit light curves from this work (left, blue) and from TK18 (right, red). The top panel shows the best fit no-moon model, and the bottom shows the best fit moon model. The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.  Each light curve is divided by its best fit systematics model (XY decorrelation for this work; second-order polynomial and offset for TK18).  The dotted gray line marks the possible moon ingress identified by TK18.}
\label{fig:bestfit}
\end{figure*}

@@

To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$. To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).  In sum, for exposure number $i$, the systematics model S is:
\begin{equation}
\label{eq:sys}
    \mathrm{S}_i = c_{j}\times(1 + a\mathrm{X}_i + b\mathrm{Y}_i) 
\end{equation}
where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. For the MCMC, we held the ramp parameters $c_1, ..., c_9$ fixed at their best-fit values.  The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for 5000 steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and confirmed that the results from the first half were consistent with the second half.

@@

We obtained a slightly better fit with the moon model (rms = 351 ppm; $\chi_\nu^2 = 0.998$); however, this is not a large enough improvement in fit quality to merit the addition of three additional free parameters.  According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 10.7$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, the moon transit time is not well-constrained by the data. As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire duration of the observations.  The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.

@@

\subsection{Comparison with Teachey \& Kipping (2018)}
\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.  To make a direct comparison with their results, we fit the raw TK18 data directly.

We fit the data with both the no-moon and models.  For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).  We therefore opted to use a TK18 systematics model to enable a fair comparison between our results. We obtained the best fit using a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model. This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}. Figure\,\ref{fig:bestfit} shows the best fit models.

Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 22.0$. Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 363 versus 356 ppm), even with the additional four free parameters.  This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.

@@

In addition to these differences in data reduction, we also used a new detrending model. We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}). We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm). We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model. The poor quality of the fit points toward the raw data as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.

 We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is in the sum of many subtle choices.

\section{Conclusion}
The hunt for exomoons remains exciting and volatile. Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling. Future allocation of follow-up resources should prioritize alternative targets.

@@

\acknowledgments
The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  %We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

@@

@@

\bibitem[{Van Der~Walt {et~al.}(2011)Van Der~Walt, Colbert, \&
  Varoquaux}]{van2011numpy}
Van Der~Walt, S., Colbert, S.~C., \& Varoquaux, G. 2011, Computing in Science
  \& Engineering, 13, 22

>>>>

\title{No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System}

\author{Laura Kreidberg}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\affiliation{Harvard Society of Fellows, 78 Mount Auburn Street, Cambridge, MA 02138}
\author{Rodrigo Luger}
\affiliation{Flatiron Institute, Simons Foundation, 162 Fifth Ave, New York, NY 10010, USA}
\author{Megan Bedell}
\affiliation{Flatiron Institute, Simons Foundation, 162 Fifth Ave, New York, NY 10010, USA}

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b I, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations, using an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$. The addition of a moon does not significantly improve the fit quality. We compare our results directly with the original light curve from \cite{teachey18b}, and find that we obtain a better fit to the data using a model with fewer free parameters (no moon). We conclude that the evidence for the transit of Kepler-1625b I hinges on subtleties of the data reduction, and we therefore suggest that future follow-up efforts for exomoons should prioritize alternate targets.

@@

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.  The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}. Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit and a possible transit timing variation \citep[][ hereafter TK18]{teachey18b}. The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.

Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method. Motivated by this result, in this work we perform an independent reduction and fit to the HST light curve.

@@

\section{Observations and Data Reduction} \label{sec:data}
The Kepler-1625 system was observed with 26 continuous \HST\ orbits on 28 - 29 October, 2017 (Program GO 15149: PI: A. Teachey). The observations used the Wide Field Camera 3 (WFC3) G141 grism in staring mode, which fixed the spectrum in a constant position on the detector.  At the beginning of the visit, there was a single exposure taken with the F130N filter, which is used to determine the position of the spectral trace. The following exposures used the G141 grism.  See TK18 for additional description of the observation design.
%with the \texttt{SPARS25}, \texttt{NSAMP}=15 readout pattern (exposure time of 290.8 seconds; 9 exposures per orbit).

We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.  This software has yielded consistent results with multiple independent pipelines \citep[e.g.][]{knutson14b, spake18}.  We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI).  In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude. We also discarded exposures taken during the South Atlantic Anomaly passage (exposures 107, 116, 125, and 126).
%The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples.

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://ane-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.  The best was $450  < \mathrm{X} < 574$, and $522 < \mathrm{Y} < 536$, where X and Y are physical pixels in the spectral and spatial direction, respectively.

We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by preferentially weighting pixels that are dominated by the target spectrum.  The inputs for optimal extraction are the background-subtracted data array, and estimate of the error per pixel, an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.  For the initial guess of the spectrum, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum.  We subtracted the background from the data array as described in \ref{sec:background}. For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction. The initial pixel mask marked all pixels as good.

To optimally extract the spectrum,  we first created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut} = 7.5$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  To create the broadband transit light curve, we sum each optimally extracted spectrum over all wavelengths. 
%This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.

@@

\subsection{Pointing Drift Measurement}
The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel/day) due to the spacecraft's pointing drift. This drift can change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons are recorded. To enable a correction for this effect, we measured the position of the spectrum over time.  Figure\,\ref{fig:shifts} shows the best fit shifts.

To measure shifts in the spatial direction, we summed each \texttt{flt} image over all columns (which we dub the ``column sum"). We used the first exposure in the visit as a template, and for each subsequent exposure, we used least-squares minimization to calculate the shift in pixels that minimized the difference between its column sum and the template. The shifts are a fraction of a pixel, so we used the NumPy \texttt{interp} routine to do linear interpolation on a sub-pixel scale. The WFC3 point spread function is undersampled, so we convolved each column sum with a 4-pixel-wide Gaussian  before the interpolation \citep[following][]{deming13}.

@@

%Over the entire 26-orbit visit, the maximum shift is less than 0.2 pixel in the spatial direction and 0.3 pixel in the spectral direction. The largest shift occurs after orbit 14, when the telescope reacquired the guide stars.

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
    \caption{Top: extractred light curve from this work (blue) compared to TK18 (red). Bottom: the difference in photoelectron counts between the data sets. The moon ingress identified by TK18 is marked by the dotted gray line.}
\label{fig:raw}
\end{figure}

\section{Analysis}
The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signals and instrument systematic noise, which we model simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}. %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.

In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the planet's time of central transit, the planet inclination, and the planet mass. For the moon model, we added a third body with six free parameters: moon radius, moon time of central transit, moon orbital period, moon inclination, moon mass, and longitude of the ascending node relative to that of the planet.  We fixed the eccentricity of all bodies to zero. We also fixed the planet's orbital period to 287.378949 days (the best fit from TK18).

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$. The moon inclination was uniform from $89.7 - 90^\circ$ (to exclude grazing moon transit scenarios, where the moon radius could be arbitrarily large). The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 180^\circ$.

\begin{figure*}
\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
    \caption{Best fit models compared to normalized transit light curves from this work (left, blue) and from TK18 (right, red). The top panel shows the best fit no-moon model, and the bottom shows the best fit moon model. The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the BIC.  Each light curve is divided by its best fit systematics model (XY decorrelation for this work; exponential and offset for TK18).  The dotted gray line marks the possible moon ingress identified by TK18.}
\label{fig:bestfit}
\end{figure*}

@@

To fit the orbit-long ramp, we used the non-parametric model from TK18, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$. To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions; shown in Figure~\ref{fig:shifts}).  In sum, for exposure number $i$, the systematics model S is:
\begin{equation}
\label{eq:sys}
    \mathrm{S}_i = c_{j}\times(1 + a\mathrm{X}_i + b\mathrm{Y}_i) 
\end{equation}
where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.

\subsection{Light Curve Fits}
We fit the broadband transit light curve using the models described above.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of the parameters. For the MCMC, we held the ramp parameters $c_1, ..., c_9$ fixed at their best-fit values.  The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for 5000 steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and confirmed that the results from the first half were consistent with the second half.

@@

We obtained a slightly lower rms with the moon model (351 ppm); however, this is not a large enough improvement in fit quality to merit the addition of six additional free parameters.  The moon model has a small increase in $\chi^2_\nu$ to 1.02. According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 26.7$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time is not unimodal, and the $2\,\sigma$ confidence interval for the moon's transit spans the entire duration of the observations.  The upper limit on the moon radius is $3.5\,R_\oplus$ at $3\sigma$ confidence.

@@

\subsection{Comparison with Teachey \& Kipping (2018)}
TK18 found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.  To make a direct comparison with their results, we fit the TK18 light curve directly.

We fit the data with both the no-moon and models.  For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).  We therefore opted to use a TK18 systematics model to enable a fair comparison between our results. We obtained the best fit using an exponential trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model. This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}. Figure\,\ref{fig:bestfit} shows the best fit models.

Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 29.9$. Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 362 versus 356 ppm), even with the additional seven free parameters.  %This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.

The mid-transit times from the two fits agree better. TK18 found that the planet transited earlier than expected based on the Kepler data. Our posterior distribution for the planet's transit time agrees with TK18 to within $1\sigma$, leaving open the possibility for transit timing variations due to another body in the system.

%, finding $t_\mathrm{planet} = 2458055.5545 \pm 0.0013$ versus $2458055.5563 \pm 0.0014\,\mathrm{BJD_{TDB}}$ from TK18.  This result leaves open the possibility for transit timing variations in the system.

@@

In addition to these differences in data reduction, we also used an alternative detrending model. We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}). We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm). We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model. The poor quality of the fit points toward the extracted light curve itself as the culprit for the difference in our results, but as we discuss, we could not identify a specific step in the data reduction that is responsible.

 We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is more likely due to the combination of many subtle choices.

\section{Conclusion}
The hunt for exomoons remains exciting and volatile. Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling. Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we suggest that future allocation of follow-up resources for exomoons should prioritize alternate targets.

@@

\acknowledgments
We thank A. Teachey for helpful discussions and for providing the extracted light curve from TK18.  The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.  
%We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.  This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.

@@

\bibitem[{{Ning} {et~al.}(2018){Ning}, {Wolfgang}, \& {Ghosh}}]{ning18}
{Ning}, B., {Wolfgang}, A., \& {Ghosh}, S. 2018, \apj, 869, 5,
  \dodoi{10.3847/1538-4357/aaeb31}

@@
